Spending too much time at the Galactic bar: chaotic fanning of the Ophiuchus stream

### 2016-01-25 ms.tex
fix links

	\begin{tabular}{ccc}
	\toprule
	$s_{\phi_2}$ [deg] & $s_{d}$ [kpc] & $s_{v_r}$ [km s$^{-1}$]\\\midrule
	$0.20\pm0.04$ & $0.31\pm0.10$ & $2.9\pm0.8$\\
	$0.21\pm0.05$ & $0.31\pm0.14$ & $3.2\pm0.9$\\
	\bottomrule
	\end{tabular}
	\caption{Estimated mean and standard deviation of samples from the marginal posterior distributions over each parameter in our orbit fit model (the posterior distributions are very close to Gaussian). For the barred potentials, all mean values are the same because the time-dependence of the bar doesn't impact the orbit fit over the short length of the stream. We have made samples from the full posterior distribution available with this article and provide code to transform to and from stream coordinates (see http://adrian.pw/ophiuchus/coordinates for more information).\label{tbl:param-means} }
\end{center}
\end{table*}

@@

\appendix
\section{Transformation from Galactic to Ophiuchus stream coordinates} \label{sec:rotationmatrix}
The transformation matrix is approximately represented as
\begin{equation*}
\left( \begin{array}{c}
x \\
y \\
z \end{array} \right)_{\rm Oph} \approx
\left( \begin{array}{ccc}
0.84922096554 & 0.07001279040 & 0.52337554476\\
-0.27043653641 & -0.79364259852 &  0.54497294023\\
0.45352820359 & -0.60434231606 & -0.65504391727
\end{array} \right) \,
\left( \begin{array}{c}
x \\
y \\
z \end{array} \right)_{\rm Gal}
\end{equation*}
but the precise transformation and coordinate frame is implemented in \python\ using the \package{Astropy} coordinates package.\footnote{See \url{http://adrian.pw/ophiuchus/coordinates} for more information}  This code is hosted on \project{GitHub}.\footnote{\url{https://github.com/adrn/ophiuchus}}

>>>>

	\begin{tabular}{ccc}
	\toprule
	$s_{\phi_2}$ [deg] & $s_{d}$ [kpc] & $s_{v_r}$ [km s$^{-1}$]\\\midrule
	$0.20\pm0.04$ & $0.31\pm0.10$ & $2.9\pm0.8$\\
	$0.21\pm0.05$ & $0.31\pm0.14$ & $3.2\pm0.9$\\
	\bottomrule
	\end{tabular}
	\caption{Estimated mean and standard deviation of samples from the marginal posterior distributions over each parameter in our orbit fit model (the posterior distributions are very close to Gaussian). For the barred potentials, all mean values are the same because the time-dependence of the bar doesn't impact the orbit fit over the short length of the stream. We have made samples from the full posterior distribution available with this article and provide code to transform to and from stream coordinates (see http://adrian.pw/ophiuchus for more information).\label{tbl:param-means} }
\end{center}
\end{table*}

@@

\appendix
\section{Transformation from Galactic to Ophiuchus stream coordinates} \label{sec:rotationmatrix}
The transformation matrix is approximately represented as
\begin{equation*}
\left( \begin{array}{c}
x \\
y \\
z \end{array} \right)_{\rm Oph} \approx
\left( \begin{array}{ccc}
0.84922096554 & 0.07001279040 & 0.52337554476\\
-0.27043653641 & -0.79364259852 &  0.54497294023\\
0.45352820359 & -0.60434231606 & -0.65504391727
\end{array} \right) \,
\left( \begin{array}{c}
x \\
y \\
z \end{array} \right)_{\rm Gal}
\end{equation*}
but the precise transformation and coordinate frame is implemented in \python\ using the \package{Astropy} coordinates package.\footnote{See \url{http://adrian.pw/ophiuchus} for more information}  This code is hosted on \project{GitHub}.\footnote{\url{https://github.com/adrn/ophiuchus}}
